\Title

### 2020-02-11 manuscript/manuscript.tex
Add block-median sources figure to manuscript

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/block-median-sources-schematics.pdf}
    \caption{
        Block-median sources. Given a set of observation points (a) we divide
        the survey region on blocks of equal size (b) and compute the median
        location of the observation points that fall inside each block.
        A source point is located beneath each block-median coordinate (c).
    }
    \label{fig:depth-types}
\end{figure*}
